---
title: "Project proposal"
author: "Data hunter"
date: "2021-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gganimate)
library(tidyverse)
library(ggplot2)
library(ggfortify)
library(dplyr)
library(tibble)
library(ggrepel)
library(GGally)

# add any other packages you need here
# if you need a package installed from github include as a comment the 
# instructions to install the package, e.g.,
# devtools::install_github("wilkelab/ggtext")
```


## Questions to be investigated

Identify a 2-3 general questions you'd like to investigate with your data visualizations. 
1. We'd like to find out whether there is a significant difference between the number of confirmed cases across countries.
2. We'd like to show out the tendency of the confirmed cases within Canada under a time series format. Specifically combined with news to explain this trend.
3. We'd like to demonstrated how the spread of COVID-19 has a exponential trend. 
4. We'd like to make a map of world that shows the heated map of the confirmed cases.
## Data to be used
Describe the data you plan to use including

Overall, the dataset tell us how many people get infected by COVID-19 under a precise time. 
It consists six csv files in total and we are planning to not use all of them, we would filter and modify it. The most visulization would be related to Canada.
The categorical variables withing this dataset are country.region and province.state quantitative variables are time, number of cases confirmed and Deaths, Recovered.
The data set is from kaggle.


Include a copy of the data in your repository in the folder called data.

Read the data into R here. Present a summary table or the output of `skimr::skim()` on your data to supplement the descriptive information you've provided.

```{r}
recorvered = time_series_covid_19_recovered%>%filter(`Country/Region`=='Canada')
confirmed = time_series_covid_19_confirmed%>%filter(`Country/Region`=='Canada')
Deaths = time_series_covid_19_deaths %>% filter(`Country/Region`=='Canada')
Canada_data = covid_19_data%>% filter(`Country/Region`=='Canada')

recorvered
confirmed
Deaths
Canada_data
```


```{r}
my_data <- read.csv("C:\\covid_19_data.csv")
my
head(my_data)
```

## Ideas for visualization

Thanks for you instructions let us learned so much in this brand new course. At the final project, I decide to perform an animated graph use the package called "gganimate". Also I will do some analysis on my data, such as regression model(plus geom_smooth), clustering and mapping my data.
To be more specific, the animated plots are meant to bring audience a vividly interaction. We can perceiving not only the overall tendency but also those slightly fluctuation from these animated plots.

The map is a strong indicator to tell the severity of the COVID-19 around the world.

Also, stationary plots are important as well. we would create mostly scatter plots to demonstrate the trend over the time series.
As we said before. To show the whole data set is too ambitious. So, we are going to filter the data into several layers and code out separately.



## Team planning
Kunhan li will be focusing on the plots making and  animation of the plot. As well as the organizing and constructing of the row data. Due to the slow speed of the internet, I want to figure out a way with professor that can ensure the success of the presentation .
Rayzhu would be mostly analysis the pca, Mds and clustering the plots. Also the powerpoint making. 


Tell me if you are both going to analyze the same dataset or if you plan to use a different dataset or subset of the dataset for each team member.

## Challenges anticipated
We do having some troubles with how to complete a reasonable regression model. Due to the fact that we are uncertain of what predictors should be set.

## References
 Source of data
## https://www.kaggle.com/sudalairajkumar/novel-corona-virus-2019-dataset


